---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# edld652

<!-- badges: start -->
[![R-CMD-check](https://github.com/datalorax/edld652/workflows/R-CMD-check/badge.svg)](https://github.com/datalorax/edld652/actions)
<!-- badges: end -->

This is course package meant to help ease the burden of downloading and 
accessing the course data. Functions will likely be added to the package as
the course goes along.

## Installation

You can install **edld652** with:

``` r
remotes::install_github("datalorax/edld652")
```

## Example

If you are a student in this class, a shared access signature (SAS) will be shared with you. This is what authenticates you to obtain access to the data. To start, you will need to pass the SAS to `set_key()` as a string (e.g., `set_key("abc-key-but-really-long-and-complicated")`). You will only need to do this once, and the package will prompt you to do this upon loading it if it hasn't been done previously. The SAS will be stored in your .REnviron (you could use something like `usethis::edit_r_environ()` if you want to see it). After running `set_key()` you will be prompted to restart R for the changes to take effect. 

Once you have stored your SAS authentication token with `set_key()`, you can import any dataset available with the `get_data()` function. However, you might be asking yourself "how do I know what file I want?". We can get a list of all available datasets with the `list_datasets()` function. For example:

```{r }
library(edld652)
list_datasets()
```

From here, we can just copy the string of the dataset we want to import and pass that to `get_data()`. For example, if we wanted to read in `"EDFacts_acgr_lea_2011_2019"`, we would use the following code

```{r }
district_grad_rates <- get_data("EDFacts_acgr_lea_2011_2019")
district_grad_rates
```

Documenation for any of these datasets is available via the `get_documentation()` function, passing the name of the dataset you'd like documentation on. Note that these will return either Microsoft Word or Excel files, which should open automatically after downloading. For example running

```{r eval = FALSE}
get_documentation("EDFacts_acgr_lea_2011_2019")
```

will create a `data-documentation` directory in your current working directory (if it does not already currently exist), download the Word or Excel file to that directory, and open the corresponding file. Running `get_documentation()` for additional datasets will add the documentation to the `data-documenatation` folder (i.e., it will not overwrite any previous documentation downloaded). Similarly, if the documentation has previously been downloaded, it will open that documentation rather than downloading the file again. In other words, running

```{r eval = FALSE}
get_documentation("NCES_CCD_nonfiscal_school_2018_membership")
```

would add (and open) a new documentation file to the `data-documentation` directory, because it is different documentation than requested previously, but running that command again would only open the file (not download it again).
